--- 
title: ""
subtitle: ""
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
bibliography: [RefsOther.bib, RefsMitigation.bib, RefsBicycle.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo:
description: "This document provides guidance on applying the Highway Capacity Manual and probe vehicle data analysis methodologies to rural highways. Rural highways are comprised of contiguous segments of multilane highway, two-lane highways, intersections (signalized, roundabout, stop control), and arterials through rural towns."
version: 1.0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if("kableExtra" %in% rownames(installed.packages()) == FALSE) {install.packages("kableExtra")} 
library(kableExtra)

TableColumnHeaderTextAngle = 0
if (knitr::is_latex_output() == TRUE){
  TableColumnHeaderTextAngle = 90
}
```


<!-- Inline comment example -->
<!-- Multiline
     comment
     example -->

<!-- If outputing to PDF, comment the material between the dashed lines. This information is included in the PDFtemplate.tex file -->

<!-- ----------------------------------- -->

# {-}

:::: {.graybox data-latex=""}
::: {.center data-latex=""}
<h2 style="text-align: center;"><b>Guidebook for Quality of Service and Reliability Analyses of Rural Highways</h2>
:::
::::

<p></p>

<p style="text-align: center;"><b>Scott S. Washburn</b></br>University of Florida</p>

<p style="text-align: center;"><b>Ahmed Al-kaisy, Sajid Raza</b></br>Montana State University</p>

<p style="text-align: center;"><b>Ana Tsui Moreno</b></br>Technical University of Munich</p>

<p style="text-align: center;"><b>Bastian Schroeder, Jorge Barrios</b></br>Kittelson & Associates, Inc.</p>

<p></p>
<p></p>

<p style="text-align: center;"><b>CRP Staff</b></br>David Jared, Senior Program Officer</p>

**NCHRP Project 08-135 Panel**

**Name**|**Role**|**Organization**|
:-----:|:-----:|:-----:|
Michael Iacono|Chair|Minnesota DOT
Mei Chen|Member|University of Kentucky
Daniel Cook|Member|HDR
Marlene Vivian Delgadillo Canizares|Member|Georgia DOT
Philip Demosthenes|Member|Philip B. Demosthenes, LLC
Jeremy Jewkes|Member|Washington State DOT
Camden Palvino|Member|Delaware Valley Regional Planning Commission
Eugene Russell|Member|Kansas State University
Taylor Sisson|Member|Vermont Agency of Transportation
Chung Tran|FHWA Liaison|FHWA

**Acknowledgements**

The research team would like to thank the following individuals for their contributions to the successful completion of this project.

Brian Dunn, Oregon Department of Transportation (retired)  
Jessie Jones, Arkansas Department of Transportation  
Ryan Kenis, University of Florida graduate student  
Emily Dang, University of Florida undergraduate student  
Jonathan Crosby, University of Florida undergraduate student  
Santiago Linares-Ramirez, Technical University of Munich graduate student  
Yangqian Cai, Technical University of Munich graduate student
Azhagan Avr, Transportation Data Analyst, Kittelson & Associates, Inc.  
Dr. Nagui Rouphail, Kittelson & Associates, Inc.
Dr. Rick Dowling, Kittelson & Associates, Inc.

**Acronyms**

AASHTO - American Association of State Highway and Transportation Officials  
HCM - Highway Capacity Manual  
FHWA - Federal Highway Administration  
HCQSC - Highway Capacity and Quality and Service Committee  
NCHRP - National Cooperative Highway Research Program  
TRB - Transportation Research Board  
USDOT - United States Department of Transportation  

<!-- ----------------------------------- -->


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 'bookdown', 'knitr', 'rmarkdown'), 'packages.bib')
```


```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

